---
title: "FAIRsimulator: Parallel study"
output:
  html_document: 
    number_sections: yes
    theme: flatly
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
      toc_depth: 3
---

# The parallel study

* Ages: 6-18 months
* Five treatments: 
    - SoC, TRT-1, TRT-2, TRT-, TRT-4 and TRT-5
    - Treatment effecs/6 months: 0.05, 0.1, 0.15, 0.20, 0.25
    - Bi-monthly observations
    - Instantaneous recruitment


```{r,message=FALSE, warning=FALSE}
library(FAIRsimulator)
set.seed(32423)
```

## Create the study

```{r}
StudyObjIni <- createStudy(
  nCohorts = 1,
  recruitmentAges = list(c(6,7)*30),
  nSubjects = c(500),
  cohortStartTimes = c(6*30),
  newCohortLink = list(NULL),
  Recruitmentfunction=function(...) {return(5000)},
  samplingDesign = list(seq(0,12,by=2)*30),
  studyStopTime = 18*30+1,
  latestTimeForNewBirthCohorts=6*30,
  treatments =list(c("SoC-1","TRT-1","TRT-2","TRT-3","TRT-4")),
  effSizes = list(c(0.05,0.1,0.15,0.20,0.25)),
  randomizationProbabilities = list(rep(0.20,5)),
  minAllocationProbabilities = list(c(0.2,rep(0,4)))
  )
```

## Run the study

The study is simulated with the `AdaptiveStudy` function.

```{r, cache=TRUE}
StudyObj <- AdaptiveStudy(StudyObjIni)
```

## Visualise the results

### The simulated HAZ data

The simulated HAZ values can be inspected using the `plotHAZ` function.

```{r}
plotHAZ(StudyObj)
```

### The randomization probabilities

```{r}
tmp <- getProbData(StudyObj,strProb = "UnWeightedUpdateProbabilities",cohortAgeNames="6-18 months")
kable(tmp %>% select(TreatmentName,Prob))
```

## Multirun

```{r multiRun,cache=TRUE}
iter   <- 100
ncores <- 7

myMultStud <- runMultiSim(StudyObjIni,iter=iter,ncores=ncores)
```

```{r,cache=TRUE}
probDf                <- myMultStud[[2]]  # The Randomization probabilities
probDfUnweightedUpdate <- getMultiProbList(myMultStud[[1]],ncores=ncores,strProb="UnWeightedUpdateProbabilities")  
```

