---
title: "Model 1"
output:
  html_document: 
    number_sections: yes
    theme: flatly
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
      toc_depth: 3
---

# Model 1

```{r,message=FALSE, warning=FALSE,echo=FALSE}
library(FAIRsimulator)
set.seed(3243)
theme_set(theme_gray(base_size=14))
```

## Treatments

* Cell 0 (SoC)
    - Counseling
    - 6 month HAZ effect: 0
* Cell 1
    - Counseling
    - Food: 7.5% PER, 10% ASP
    - Iron + Vitamin A + Zinc
    - 6 month HAZ effect: 0.0633
* Cell 2
    - Counseling
    - Food: 15% PER, 30% ASP
    - Multiple micronutrient supplementation
    - 6 month HAZ effect: 0.1037
* Cell 3
    - Counseling
    - Food: 15% PER, 30% ASP
    - Multiple micronutrient supplementation
    - Antibiotics + Probiotics
    - 6 month HAZ effect: 0.1574
* Cell 4
    - Counseling
    - Food: 15% PER, 30% ASP
    - Multiple micronutrient supplementation
    - Antibiotics + Probiotics
    - WASH Intensified
    - Psychosocial care and support
    - 6 month HAZ effect: 0.1687

## Study design settings

These study design options were used for the current set of simulations:

* 3 recruitment cycles: 0, 6, and 12 months (study time).
* 2 recruitment age groups: 6 and 12 months (age).
* Instantaneous recruitment (all children recruited on day 1).
* The initial randomization set to 1:1:1:1:1.
* The minimum randomization probability for SoC is 20%.
* Treatment arms with a probability less than 10% *before* adjusting for the minimum SoC randomization probability is dropped.
* All available data up and including the timepoint for the interim analyses is used to update the probabilities.
* The dropout rate is approximately 20%/6 months.
* Bi-monthly HAZ observations.
* Interim analyses every 6 months.
* Square root probability updates (small probabilities are inflated)

```{r, echo=FALSE,cache=TRUE,message=FALSE,warning=FALSE,results="hide"}

## One adapted cohort
AddNewSixMonthCohortEvent<-function(StudyObj) {
  #Note - assuming birth cohort is first element in StudyDesignSettings
  
  if (!is.null(StudyObj$CohortList)) {
    for (i in 1:length(StudyObj$CohortList)) {
      Cohort<-StudyObj$CohortList[[i]]
      if ((Cohort$Active==FALSE && 
           Cohort$RandomizationAgeRange[1]==6*30 && 
           Cohort$CycleNum==1 && 
           Cohort$CohortStartTime+Cohort$CurrentTime==StudyObj$CurrentTime && 
           StudyObj$CurrentTime<=StudyObj$StudyDesignSettings$LatestTimeForNewBirthCohorts) || #If this cohort just ended and its time to add a new cohort
            (Cohort$Active==TRUE && 
             Cohort$RandomizationAgeRange[1]==6*30 && 
             Cohort$CycleNum==1 && 
             Cohort$CohortStartTime+6*30==StudyObj$CurrentTime && 
             StudyObj$CurrentTime<=StudyObj$StudyDesignSettings$LatestTimeForNewBirthCohorts))
        {
        BirthCohortIndex<-which(unlist(lapply(StudyObj$StudyDesignSettings$CohortAgeRange,function(x) {x[1]==6*30}))==TRUE) #Get the birth cohort index (i.e. lower AgeRangeAtRandomization=0)
        NewChildCohort<-NewCohort(StudyObj,CohortNum=BirthCohortIndex)
        NewChildCohort$StartNum <- max(StudyObj$CohortList %listmap% "StartNum")+1
        NewChildCohort$Name<-paste0("C-",NewChildCohort$StartNum,"-",1," [",Cohort$RandomizationAgeRange[1]/30,"-",Cohort$RandomizationAgeRange[2]/30,"m @ rand]")
        DebugPrint(paste0("Create new 6 month cohort ",NewChildCohort$Name," based on probabilities in ",Cohort$Name," at time: ",StudyObj$CurrentTime),1,StudyObj)
        NewChildCohort$RandomizationProbabilities<-Cohort$UpdateProbabilities #Use the latest probabilities from previous birth cohort
        NewChildCohort$UnWeightedRandomizationProbabilities<-Cohort$UnWeightedUpdateProbabilities
        StudyObj$CohortList[[(length(StudyObj$CohortList)+1)]]<-NewChildCohort
        break
      }
    }
  }
  return(StudyObj)
}

## One adapted cohort
AddNewTwelveMonthCohortEvent<-function(StudyObj) {
  #Note - assuming birth cohort is first element in StudyDesignSettings
  
  if (!is.null(StudyObj$CohortList)) {
    for (i in 1:length(StudyObj$CohortList)) {
      Cohort<-StudyObj$CohortList[[i]]
      if (Cohort$Active==FALSE && Cohort$RandomizationAgeRange[1]==12*30 && Cohort$CycleNum==1 && Cohort$CohortStartTime+Cohort$CurrentTime==StudyObj$CurrentTime && StudyObj$CurrentTime<=StudyObj$StudyDesignSettings$LatestTimeForNewBirthCohorts) #if this cohort just ended and its time to add a new cohort
      {
        BirthCohortIndex<-which(unlist(lapply(StudyObj$StudyDesignSettings$CohortAgeRange,function(x) {x[1]==12*30}))==TRUE) #Get the birth cohort index (i.e. lower AgeRangeAtRandomization=0)
        NewChildCohort<-NewCohort(StudyObj,CohortNum=BirthCohortIndex)
        NewChildCohort$StartNum <- max(StudyObj$CohortList %listmap% "StartNum")+1
        NewChildCohort$Name<-paste0("C-",NewChildCohort$StartNum,"-",1," [",Cohort$RandomizationAgeRange[1]/30,"-",Cohort$RandomizationAgeRange[2]/30,"m @ rand]")
        DebugPrint(paste0("Create new 12 month cohort ",NewChildCohort$Name," based on probabilities in ",Cohort$Name," at time: ",StudyObj$CurrentTime),1,StudyObj)
        NewChildCohort$RandomizationProbabilities<-Cohort$UpdateProbabilities #Use the latest probabilities from previous birth cohort
        NewChildCohort$UnWeightedRandomizationProbabilities<-Cohort$UnWeightedUpdateProbabilities
        StudyObj$CohortList[[(length(StudyObj$CohortList)+1)]]<-NewChildCohort
        break
      } 
        
    }
  }
  return(StudyObj)
}


probTemperation <- function(probs) {
  probs <- sqrt(probs)/sum(sqrt(probs))
  return(probs)
}

InterimAnalyzesTime<-function(Cohort,StudyObj) {
  DebugPrint(paste0("Check if cohort ",Cohort$Name," is about to have an interim analysis",StudyObj$CurrentTime),3,StudyObj)
  TimeToPerformInterim<-FALSE
  tmp<-sum(unlist(lapply(Cohort$SubjectList,function(Subject,LastSample){
    return(as.numeric(Subject$Status==0 || (LastSample %in% Subject$SubjectSampleTime)))},max(Cohort$SamplingDesign))))/Cohort$MaxNumberOfSubjects
  if (length(tmp)==0) tmp<-0
  
  if (Cohort$RandomizationAgeRange[1]==6*30 && (StudyObj$CurrentTime==6*30-1 || StudyObj$CurrentTime==18*30-1 )) {
    DebugPrint(paste0("Time to do an interim analyses for cohort ",Cohort$Name," at time: ",StudyObj$CurrentTime," (",round(tmp*100,1)," % subjects completed)"),1,StudyObj)
    TimeToPerformInterim<-TRUE
  }
  return(TimeToPerformInterim)
}

FinalAnalysesEvent<-function(StudyObj) {
  DebugPrint(paste0("Check if time to do a final analyses at study time: ",StudyObj$CurrentTime),3,StudyObj)
  if (StudyObj$CurrentTime==StudyObj$StudyDesignSettings$StudyStopTime-1) {
    DebugPrint(paste0("Time to do a final analyses with all data at time: ",StudyObj$CurrentTime),1,StudyObj)
    df<-getAllSubjectData(StudyObj,prevTreatment = TRUE) #Get all data that is neede for final analyses
    ## Rename, select and order columns
    if(length(names(df)[grep(names(df),pattern = "PTRT")]) >0) {
      df <- df %>% 
        rename(ID=StudyID,DATA=HAZ,AGE=Age,TRT=TreatmentIndex,TRTS=Treatment) %>% 
        select(ID,DATA,AGE,TRT,TRTS,one_of(StudyObj$StudyDesignSettings$Covariates),Level,CohortName,matches("PTRT"))
      for (cstr in names(df)[grep(names(df),pattern = "PTRT")]) { #Set no previous treatment to "0"
        df[,cstr]<-ifelse(is.na(df[,cstr]),0,df[,cstr])
      }
    } else {
      df <- df %>% 
        rename(ID=StudyID,DATA=HAZ,AGE=Age,TRT=TreatmentIndex,TRTS=Treatment) %>% 
        select(ID,DATA,AGE,TRT,TRTS,one_of(StudyObj$StudyDesignSettings$Covariates),Level,CohortName)
    }
    
    df[df==-99]<-NA #Set -99 to missing
    df<-ImputeCovariates(df,StudyObj,method=StudyObj$StudyDesignSettings$ImpMethod) #Impute missing covariates
    
    #Sort to get correct TRT order
    df <- df[order(df["TRT"],df["ID"], df["AGE"]),] 
    
    ##### Make some covariate factors
    df$TRT<-as.factor(df$TRT) 
    df$SEXN<-as.factor(df$SEXN)
    df$SANITATN<-as.factor(df$SANITATN)
    df$AGE<-df$AGE/(12*30) #Rescale time to years
    
    ### If we have previous treatments
    ptrti <- grep("PTRT",names(df))
    if(length(ptrti)>0) {
      
      for(i in 1:length(ptrti)) {
        df[,ptrti[i]] <- as.factor(df[,ptrti[i]])
      }
      myPTRTs <- names(df)[ptrti]
    }
    
    cohortlevels<-unique(StudyObj$CohortList %listmap% "Level")
    
    for (l in 1:length(cohortlevels)) {
      dflevel<-subset(df,Level==cohortlevels[l])
      
      #### Perform LME estimation based on some covariates and treatment effects for each level
      if(length(ptrti)>0) {
        
        lmeFormula <- paste0("DATA~1 + AGE + AGE:TRT + (AGE|ID) +",paste0(c(StudyObj$StudyDesignSettings$Covariates,myPTRTs),collapse = " + "))
      } else {
        lmeFormula <- paste0("DATA~1 + AGE + AGE:TRT + (AGE|ID) +",paste0(StudyObj$StudyDesignSettings$Covariates,collapse = " + "))
      }
      
      lmefit <- lmer(lmeFormula,data=dflevel,REML=FALSE) # IIV on baseline only
      
      ##### Calculate new probabilites based on another cohort LME results
      lmecoef<-summary(lmefit)$coefficients[,1] #Get coefficicents from LME
      lmese<-summary(lmefit)$coefficients[,2] #Get SE from LME
      lmecoef<-lmecoef[regexpr('AGE:TRT.*',names(lmecoef))==1]
      lmese<-lmese[regexpr('AGE:TRT.*',names(lmese))==1]
      print(lmefit)
      ### Get first cohort with level = l
      if (!is.null(StudyObj$CohortList)) {
        for (i in 1:length(StudyObj$CohortList)) {
          if (StudyObj$CohortList[[i]]$Level==l) {
            Cohort<-StudyObj$CohortList[[i]]
            break
          }
        }

        if ((length(lmecoef)+1)!=length(Cohort$RandomizationProbabilities)) {
          lmecoefnew<-rep(0,length(Cohort$RandomizationProbabilities)-1)
          lmesenew<-rep(0,length(Cohort$RandomizationProbabilities)-1)
          for (i in 1:(length(Cohort$RandomizationProbabilities)-1)) {
            iIndex<-which(names(lmecoef)==paste0("AGE:TRT",i+1))
            if (length(iIndex)!=0) {
              lmecoefnew[i]<-lmecoef[iIndex]
              lmesenew[i]<-lmese[iIndex]
            }
          }
          names(lmecoefnew)<-paste0("AGE:TRT",2:length(Cohort$RandomizationProbabilities))
          names(lmesenew)<-paste0("AGE:TRT",2:length(Cohort$RandomizationProbabilities))
          lmecoef<-lmecoefnew
          lmese<-lmesenew
        }
      }
      #Get probability of beeing best
      probs <- GetNewRandomizationProbabilities(trtcoeff=lmecoef,trtse=lmese,
                                                StudyObj$StudyDesignSettings$iNumPosteriorSamples) #Calculate randomization probs based on posterior distribution
      
      ## Apply any probability temperation function, e.g. sqrt
      probstemp <- StudyObj$StudyDesignSettings$probTemperation(probs)
    
      ## Save finala analyses output
      FinalAnalyses<-list()
      
      FinalAnalyses$Level = l
      FinalAnalyses$Time = StudyObj$CurrentTime
      FinalAnalyses$LMEFit<-lmefit
      FinalAnalyses$UnWeightedUpdateProbabilities<-probs
      FinalAnalyses$UnWeightedTemperatedUpdateProbabilities<-probstemp
      FinalAnalyses$LMECoeff<-lmecoef
      FinalAnalyses$LMESE<-lmese
      StudyObj$FinalAnalysesList[[length(StudyObj$FinalAnalysesList)+1]]<-FinalAnalyses
      
      ## Also add probabilities and coeffs on the StudyObj level
      StudyObj$FinalUnWeightedUpdateProbabilities<-probs
      StudyObj$LMECoeff<-lmecoef
    }
  }
  return(StudyObj)
}

StudyObjIni <- createStudy(
  nCohorts                       = 2,
  recruitmentAges                = list(c(6,7)*30,c(12,13)*30),
  nSubjects                      = c(500,500),
  cohortStartTimes               = c(0*30,0*30),
  newCohortLink                  = list(NULL,NULL),
  Recruitmentfunction            = function(...) {return(5000)},
  samplingDesign                 = list(seq(0,12,by=2)*30,seq(0,6,by=2)*30),
  studyStopTime                  = 18*30+5,
  latestTimeForNewBirthCohorts   = 14*30+1,
  treatments                     = list(c("SoC-1","Cell 1","Cell 2"," Cell 3"," Cell 4"),c("SoC-1","Cell 1","Cell 2"," Cell 3"," Cell 4")),
  effSizes                       = list(c(0,0.0633,0.1037,0.1574,0.1687),c(0,0.0633,0.1037,0.1574,0.1687)),
  randomizationProbabilities     = list(rep(0.20,5),rep(0.20,5)),
  minAllocationProbabilities     = list(c(0.2,rep(0,4)),c(0.2,rep(0,4))),
  probTemperationFunction        = probTemperation,
  AddNewBirthCohortEventFunction = AddNewSixMonthCohortEvent,
  interimAnalyzesTimeFunction    = InterimAnalyzesTime,
  accumulatedData = TRUE
)

StudyObjIni$EventList[[length(StudyObjIni$EventList)+1]]<-AddNewTwelveMonthCohortEvent
StudyObjIni$EventList[[length(StudyObjIni$EventList)+1]]<-FinalAnalysesEvent


StudyObj <- AdaptiveStudy(StudyObjIni)
```

```{r,warning=FALSE,message=FALSE,echo=FALSE}

p <- plotStudyCohorts(StudyObj,plotAnaTimes = T,shiftWithinLevel = 1)

p + scale_y_continuous(breaks=c(7.5,13.5),labels=c("6-18 months","12-18 months")) +
  ylab(NULL) +
  theme(legend.position="none")
```

## Results


The simulated HAZ data.

```{r,echo=FALSE}
allData <- getAllSubjectData(StudyObj,scalarItems="AgeAtRand",covariates=NULL) 

allData$Cohort2 <- as.character(allData$Cohort)
allData$Cohort2 <- factor(allData$Cohort2,levels=c("Cohort 2","Cohort 4","Cohort 6","Cohort 1","Cohort 3","Cohort 5"))
plotHAZ(StudyObj,data=allData) + aes(color=Cohort) + facet_wrap(~Cohort2) + theme(legend.position="none") + scale_x_continuous(breaks=c(6,12,18))
```

The randomization probabilties **before*** adjusting for the minimum SoC randomization probability.

```{r,warning=FALSE,echo=FALSE,message=FALSE,error=FALSE,fig.width=9}
plotProbs(StudyObj,cohortAgeNames=c("6-18 months","12-18 months"),strProb="UnWeightedRandomizationProbabilities")
```


The randomization probabilties **after** adjusting for the minimum SoC randomization probability.

```{r,warning=FALSE,echo=FALSE,message=FALSE,error=FALSE,fig.width=9}
plotProbs(StudyObj,cohortAgeNames=c("6-18 months","12-18 months"),strProb="RandomizationProbabilities")
```

The final analysis of all the data gives the following probabilities:

```{r, echo=FALSE}
finalProbDf <- data.frame(Treatment=StudyObj$StudyDesignSettings$Treatments[[1]],
                          Col1= StudyObj$FinalAnalysesList[[1]]$UnWeightedUpdateProbabilities,
                          Col2= StudyObj$FinalAnalysesList[[2]]$UnWeightedUpdateProbabilities)

kable(finalProbDf,dig=2,col.names=c("Treatment","Prob 6-18 months","Prob 12-18 months"))
```

The final analysis of all the data gives the following estimated treatment effects (change in HAZ/6 months):

```{r, echo=FALSE}
finalCoefDf <- data.frame(Treatment=(StudyObj$StudyDesignSettings$Treatments[[1]])[-1],
                          Col1= StudyObj$FinalAnalysesList[[1]]$LMECoeff/2,
                          Col2= StudyObj$FinalAnalysesList[[2]]$LMECoeff/2)

kable(finalCoefDf,dig=2,col.names=c("Treatment","Eff 6-18 months","Eff 12-18 months"),row.names=FALSE)
```


## Repeating the study multiple times

```{r runMult,multiRun,cache=TRUE,warning=FALSE,echo=FALSE}
iter   <- 2
ncores <- 7

myMultStud <- runMultiSim(StudyObjIni,iter=iter,ncores=ncores,cohortAgeNames=c("6-18 months","12-18 months"),strProb="UnWeightedRandomizationProbabilities")
```

```{r getProbs, cache=TRUE,dependson="runMult",echo=FALSE}
probDfUnWeightedRandProb <- myMultStud[[2]]
probDfRandProb <- getMultiProbList(myMultStud[[1]],cohortAgeNames=c("6-18 months","12-18 months"),strProb="RandomizationProbabilities",ncore=ncores)
```

Running the study multiple time (in this case **`r iter` times**) allows for the computation of performance statistics.

The randomization probabilties *after* adjusting for the minimum SoC randomization probability. The shaded areas are the 95% prediction intervals.

```{r,dependson="getProbs",echo=FALSE,fig.width=10}
plotMultiProb(probDfUnWeightedRandProb)
```

The randomization probabilties after adjusting for the minimum SoC randomization probability. The shaded areas are the 95% prediction intervals.

```{r,dependson="getProbs",echo=FALSE,fig.width=10}
plotMultiProb(probDfRandProb)
```


### Performance metrics

To compare design choices quantitatively it is useful with performance metrics. Two suggestions are the randomization probabilities based on an analysis of all data (i.e. at the end of the trial) and the estimated treatment effects based on all data.

```{r, echo=FALSE}

trtNams1 <- c("SoC-1","Cell1", "Cell2","Cell3","Cell4")


nStud <- length(myMultStud[[1]])

dfProbs1 <- data.frame(matrix(0,nrow=nStud,ncol=length(trtNams1)))
dfCoeff1 <- dfProbs1
dfProbs2 <- data.frame(matrix(0,nrow=nStud,ncol=length(trtNams1)))
dfCoeff2 <- dfProbs2

for(i in 1:length(myMultStud[[1]])) {
  dfProbs1[i,] <- myMultStud[[1]][[i]]$FinalAnalysesList[[1]]$UnWeightedUpdateProbabilities
  dfProbs2[i,] <- myMultStud[[1]][[i]]$FinalAnalysesList[[2]]$UnWeightedUpdateProbabilities
  
  dfCoeff1[i,] <- c(0,myMultStud[[1]][[i]]$FinalAnalysesList[[1]]$LMECoeff)
  dfCoeff2[i,] <- c(0,myMultStud[[1]][[i]]$FinalAnalysesList[[2]]$LMECoeff)
}

names(dfProbs1) <- trtNams1
names(dfProbs2) <- trtNams1
names(dfCoeff1) <- trtNams1
names(dfCoeff2) <- trtNams1

dfProbs1$AgeGroup <- "6-18 months"
dfProbs2$AgeGroup <- "12-18 months"

dfCoeff1$AgeGroup <- "6-18 months"
dfCoeff2$AgeGroup <- "12-18 months"

dfProbs <- rbind(dfProbs1,dfProbs2)
dfCoeff <- rbind(dfCoeff1,dfCoeff2)


sumFinProb <- 
  dfProbs %>% gather("Treatment","Probability",-AgeGroup) %>% 
  mutate(Treatment = factor(Treatment,levels=trtNams1),AgeGroup=factor(AgeGroup,levels=c("6-18 months","12-18 months"))) %>% 
  group_by(Treatment,AgeGroup) %>% 
  summarise(
    Mean = mean(Probability),
    Low=quantile(Probability,p=0.025),
    High=quantile(Probability,p=0.975))



sumFinProbPow <- dfProbs

for(i in 1:nrow(sumFinProbPow)) {
  sumFinProbPow$Pow1[i] <- ifelse(sumFinProbPow$Cell1[i] == max(sumFinProbPow$Cell1[i],sumFinProbPow$Cell2[i],sumFinProbPow$Cell3[i],sumFinProbPow$Cell4[i]),1,0)
  sumFinProbPow$Pow2[i] <- ifelse(sumFinProbPow$Cell2[i] == max(sumFinProbPow$Cell1[i],sumFinProbPow$Cell2[i],sumFinProbPow$Cell3[i],sumFinProbPow$Cell4[i]),1,0)
  sumFinProbPow$Pow3[i] <- ifelse(sumFinProbPow$Cell3[i] == max(sumFinProbPow$Cell1[i],sumFinProbPow$Cell2[i],sumFinProbPow$Cell3[i],sumFinProbPow$Cell4[i]),1,0)
  sumFinProbPow$Pow4[i] <- ifelse(sumFinProbPow$Cell4[i] == max(sumFinProbPow$Cell1[i],sumFinProbPow$Cell2[i],sumFinProbPow$Cell3[i],sumFinProbPow$Cell4[i]),1,0)
}


sumFinProbPow2 <- sumFinProbPow %>% 
  select(AgeGroup,Pow1:Pow4) %>% 
  dplyr::rename(Cell1=Pow1,Cell2=Pow2,Cell3=Pow3,Cell4=Pow4) %>% 
  gather("Treatment","value",-AgeGroup) %>% 
  group_by(Treatment,AgeGroup) %>% 
  summarise(Power=sum(value/n())) %>% 
  filter(Treatment=="Cell4")
  
sumFinCoeff <- 
  dfCoeff %>% gather("Treatment","Coeff",-AgeGroup) %>% 
  mutate(Treatment = factor(Treatment,levels=trtNams1),Effect = Coeff/2,AgeGroup=factor(AgeGroup,levels=c("6-18 months","12-18 months"))) %>% 
  group_by(Treatment,AgeGroup) %>% 
  summarise(
    Mean = mean(Effect),
    Low  = Mean - 1.96*sd(Effect)/sqrt(n()),
    High   = Mean + 1.96*sd(Effect)/sqrt(n()))

```

The "power" for Cell4 to be the best treatment in the two age groups are:

```{r echo=FALSE}
kable(sumFinProbPow2,dig=2)
```


The randomization probabilities (the bars are 95% prrdiction intervals):
```{r, echo=FALSE}
ggplot(sumFinProb,aes(Treatment,Mean,color=Treatment)) +
  geom_point() +
  theme(legend.position="none") +
  geom_errorbar(aes(ymin=Low,ymax=High),width=0.2) +
  facet_wrap(~AgeGroup)
```

The treatment effects/6 months (the black dots are the true effects an the bars are 95% CI).
```{r, echo=FALSE}

trueEff <- data.frame(Treatment=trtNams1,Mean=c(0,0.0633,0.1037,0.1574,0.1687))
ggplot(sumFinCoeff,aes(Treatment,Mean,color=Treatment)) +
  geom_point() +
  geom_point(data=trueEff,color="black") +
  theme(legend.position="none") +
  geom_errorbar(aes(ymin=Low,ymax=High),width=0.2) +
  facet_wrap(~AgeGroup)
```
