---
title: "FAIRsimulator"
author: "Niclas Jonsson and Joakim Nyberg"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  \VignetteIndexEntry{FAIRsimulator}
  %\VignetteEngine{knitr::rmarkdown}
  \VignetteEncoding{UTF-8}
---

```{r,message=FALSE, warning=FALSE}
library(FAIRsimulator)
```


## Run a simulaiton

Assume there is a a FAIRsimulator study object available.

```{r}
# Run the simulations in the exampel file
#source("../FAIRstudy.R",echo=FALSE)
load("../studyobj.Rdata")
```

## Results

### Visualise the design

```{r,fig.width=6}

plotStudyCohorts(StudyObj)

```

## Visualise the number of subjects in each cohort over time.

The number of subjects in each cohort is the result of recruitment rate, dropout and completion (i.e. being moved to the next cycle).

```{r,fig.width=6}
plotActiveSubjects(StudyObj)
```

### Visualise the simulated HAZ data

```{r,fig.width=6}
plotHAZ(StudyObj)
```

### Visualise the treatment effects

```{r,fig.width=8,fig.height=8}
plotHAZTreatmentEff(StudyObj)
```

### List the randomization probabilities

Each cohort has a set of randomization probabilities. When subjects move to later cycles, they get assigned to new treatments according to probabilities that have been
updated based on the previous cohort in the same age range. The randomization probabilities can be listed:

```{r}
kable(StudyObj$CohortList %listmap% "RandomizationProbabilities",digits = 2)
```


### List the updated randomization probabilities

Once a study is finished, each cohort have updated randomization probabilities. These probabilities are available even if they were never used to inform
the randomization of treatments in other cohorts. For example Cohort 1 in Cycle 3 will not inform the randomization in any other cohorts, since there are no 
cohorts following it.

```{r}
kable(StudyObj$CohortList %listmap% "UpdateProbabilities",digits=2)


StudyObj$CohortList[[4]]$PreviousRandomizationProbabilities
```


